---
title: "CSI 777 Plots"
author: "Thomas W. Jones"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 8, fig.height = 6, cache = TRUE)
```

## Simulation: No interactions

```{r}

rm(list = ls())

source("R/00_common_functions.R")

load("data_derived/no_interactions.RData")

# Prepare charts
linear_effects <- list(baseline = summary(mfx_linear, print = F),
                       rf = summary(mfx_rf_linear, print = F),
                       nn = summary(mfx_nn_linear, print = F))

lin_plot <- rbind(baseline = linear_effects$baseline$effect,
                  rf = linear_effects$rf$effect,
                  nn = linear_effects$nn$effect)

colnames(lin_plot) <- linear_effects[[ 1 ]]$variable

barplot(lin_plot, beside = TRUE,
        col = c("#66c2a5", "#fc8d62", "#8da0cb"),
        main = "Simple Linear Simulation",
        ylab = "Marginal Effect")

legend("topleft",
       legend = paste0(c("Baseline", "Random Forest", "Neural Network"), 
                      " (", round(unlist(linear_eval), 3), ")"),
       fill = c("#66c2a5", "#fc8d62", "#8da0cb"))


knitr::kable(t(lin_plot), digits = 3)


logit_effects <- list(baseline = summary(mfx_logit, print = F),
                       rf = summary(mfx_rf_logit, print = F),
                       nn = summary(mfx_nn_logit, print = F))

log_plot <- rbind(baseline = logit_effects$baseline$effect,
                  rf = logit_effects$rf$effect,
                  nn = logit_effects$nn$effect)

colnames(log_plot) <- logit_effects[[ 1 ]]$variable

barplot(log_plot, beside = TRUE,
        col = c("#66c2a5", "#fc8d62", "#8da0cb"),
        main = "Simple Logistic Simulation",
        ylab = "Marginal Effect")

legend("topleft",
       legend = paste0(c("Baseline", "Random Forest", "Neural Network"),
                      " (", round(sapply(logit_eval, function(x) x$auc), 3), ")"),
       fill = c("#66c2a5", "#fc8d62", "#8da0cb"))

knitr::kable(t(log_plot), digits = 3)


```

### Baseline Linear ICE Plots

```{r}
plot(mfx_linear, ask = FALSE, ylim = c(-40, 60), main = "Baseline Model")
```

### Random Linear Forest ICE Plots

```{r}
plot(mfx_rf_linear, ask = FALSE, ylim = c(-40, 60), main = "Random Forest")
```

### Neural Network Linear ICE Plots

```{r}
plot(mfx_nn_linear, ask = FALSE, ylim = c(-40, 60), main = "Neural Network")
```

### Baseline Logistic ICE Plots

```{r}
plot(mfx_logit, ask = FALSE, ylim = c(0, 1), 
     main = "Baseline Model")
```

### Random Forest Logistic ICE Plots

```{r}
plot(mfx_rf_logit, ask = FALSE, ylim = c(0, 1), 
     main = "Random Forest")
```

### Neural Network Logistic ICE Plots

```{r}
plot(mfx_nn_logit, ask = FALSE, ylim = c(0, 1), 
     main = "Neural Network")
```




## Simulation: Interaction + Quadratic

```{r}
rm(list = ls())

source("R/00_common_functions.R")

load("data_derived/one_interaction.RData")

# Linear
linear_effects <- list(baseline = summary(mfx_linear, print = F),
                       lasso = summary(mfx_linear_all, print = F),
                       rf = summary(mfx_rf_linear, print = F),
                       nn = summary(mfx_nn_linear, print = F))


lin_plot <- merge(linear_effects[[ 1 ]][ , c("variable", "effect") ], 
                  linear_effects[[ 2 ]][ , c("variable", "effect") ],
                  by = "variable", all = TRUE)

for( j in 3:length(linear_effects)) 
  lin_plot <- merge(lin_plot,
                    linear_effects[[ j ]][ , c("variable", "effect")],
                    by = "variable", all = TRUE) 

names(lin_plot)[ 2:ncol(lin_plot) ] <- c("baseline", "lasso", "rf", "nn")

ln <- lin_plot$variable

lin_plot <- t(lin_plot[ , 2:ncol(lin_plot) ])

colnames(lin_plot) <- ln

lin_plot <- lin_plot[ , linear_effects$lasso$variable ]

barplot(lin_plot, beside = TRUE,
        col = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3"),
        main = "Linear Simulation with Interactions",
        ylab = "Marginal Effect",
        ylim = c(-3, 4))

legend(list(x = 0, y = -0.05),
       legend = paste0(c("Baseline", "Lasso", "Random Forest", "Neural Network"),
                       " (", round(unlist(linear_eval), 3), ")"),
       fill = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3"))

knitr::kable(t(lin_plot), digits = 3)


# Logit
logit_effects <- list(baseline = summary(mfx_logit, print = F),
                       lasso = summary(mfx_logit_all, print = F),
                       rf = summary(mfx_rf_logit, print = F),
                       nn = summary(mfx_nn_logit, print = F))


log_plot <- merge(logit_effects[[ 1 ]][ , c("variable", "effect") ], 
                  logit_effects[[ 2 ]][ , c("variable", "effect") ],
                  by = "variable", all = TRUE)

for( j in 3:length(logit_effects)) 
  log_plot <- merge(log_plot,
                    logit_effects[[ j ]][ , c("variable", "effect")],
                    by = "variable", all = TRUE) 

names(log_plot)[ 2:ncol(log_plot) ] <- c("baseline", "lasso", "rf", "nn")

ln <- log_plot$variable

log_plot <- t(log_plot[ , 2:ncol(log_plot) ])

colnames(log_plot) <- ln

log_plot <- log_plot[ , logit_effects$lasso$variable ]

barplot(log_plot, beside = TRUE,
        col = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3"),
        main = "Logistic Simulation with Interactions",
        ylab = "Marginal Effect",
        ylim = c(-0.05, 0.15))

legend("topleft",
       legend = paste0(c("Baseline", "Lasso", "Random Forest", "Neural Network"),
                       " (", round(sapply(logit_eval, function(x) x$auc), 3), ")"),
       fill = c("#66c2a5", "#fc8d62", "#8da0cb", "#e78ac3"))

knitr::kable(t(log_plot), digits = 3)
```

### Baseline Linear ICE Plots

```{r}
plot(mfx_linear, ask = FALSE, ylim = c(-200, 150), main = "Baseline Model")
```

### Lasso Linear ICE Plots

```{r}
plot(mfx_linear_all, ask = FALSE, ylim = c(-200, 150), main = "Lasso Model")

```


### Random Linear Forest ICE Plots

```{r}
plot(mfx_rf_linear, ask = FALSE, ylim = c(-200, 150), main = "Random Forest")
```

### Neural Network Linear ICE Plots

```{r}
plot(mfx_nn_linear, ask = FALSE, ylim = c(-200, 150), main = "Neural Network")
```

### Baseline Logistic ICE Plots

```{r}
plot(mfx_logit, ask = FALSE, ylim = c(0, 1), main = "Baseline Model")
```

### Lasso Linear ICE Plots

```{r}
plot(mfx_logit_all, ask = FALSE, ylim = c(0, 1), main = "Lasso Model")

```

### Random Forest Logistic ICE Plots

```{r}
plot(mfx_rf_logit, ask = FALSE, ylim = c(0, 1), main = "Random Forest")
```

### Neural Network Logistic ICE Plots

```{r}
plot(mfx_nn_logit, ask = FALSE, ylim = c(0, 1), main = "Neural Network")
```

## NASS/CDS Dataset

```{r}

rm(list = ls())

source("R/00_common_functions.R")

load("data_derived/real_data.RData")

# Prepare charts
effects <- list(lasso = summary(mfx_lasso, print = F),
                       rf = summary(mfx_rf, print = F))

log_plot <- rbind(lasso = effects$lasso$effect,
                  rf = effects$rf$effect)

colnames(log_plot) <- effects[[ 1 ]]$variable

eval <- lapply(model_accuracy[ c("lasso", "rf")], function(x){
  sapply(x, function(y) y$auc)
})

log_plot <- log_plot[ , order(colMeans(abs(log_plot))) ]

log_plot <- log_plot[ , setdiff(colnames(log_plot), "bmode_Unk") ]

par(mar = c(7, 4, 4, 2) + .1)

barplot(log_plot, beside = TRUE,
        col = c("#66c2a5", "#fc8d62"),
        main = "Predicting Severe Injury",
        ylab = "Marginal Effect",
        las = 2)

legend("topleft",
       legend = paste0(c("Lasso", "Random Forest"),
                      " (", round(sapply(eval, mean), 3), ")"),
       fill = c("#66c2a5", "#fc8d62"))

# make a table of coefficients
table_out <- lapply(effects, function(x) x[ , c("effect", "t_stat") ])

# for (j in seq_along(table_out)) {
#   colnames(table_out[[ j ]]) <- paste(names(table_out)[ j ], 
#                                       colnames(table_out[[ j ]]),
#                                       sep = "\n")
# }

table_out <- do.call(cbind, table_out)

table_out <- table_out[ order(abs(table_out[ , 1 ]), decreasing = TRUE) , ]

knitr::kable(table_out, digits = 3)

```

### Lasso Linear ICE Plots

```{r}
plot(mfx_lasso, ask = FALSE, main = "Lasso Model", ylim = c(0, 1))

```

### Random Forest Logistic ICE Plots

```{r}
plot(mfx_rf, ask = FALSE, main = "Random Forest", ylim = c(0, 1))
```

### Compare lasso coefficients with mfx


```{r}

lasso_table <- broom::tidy(model_lasso)

lasso_table <- lasso_table[ lasso_table$step == max(lasso_table$step) , ]

result <- merge(lasso_table[ , c("term", "estimate") ],
                effects$lasso[ , c("variable", "effect") ],
                by.x = "term", by.y = "variable")

result$estimate <- result$estimate / max(abs(result$estimate))

result$effect <- result$effect / max(abs(result$effect))

names(result)[ 2:3 ] <- c("coef", "mfx")

rownames(result) <- result$term

result <- result[ order(rowMeans(abs(result[ , 2:3 ]))) , ]

result <- t(result[ , 2:3 ])

par(mar = c(7, 4, 4, 2) + .1)

barplot(result, beside = TRUE,
        col = c("#66c2a5", "#fc8d62"),
        main = "Coefficient vs. Marginal Effect\nin Lasso Model",
        ylab = "Estimate / (Max Absolute Estimate)",
        las = 2)

legend("topleft",
       legend = c("Coefficient", "Marginal Effect"),
       fill = c("#66c2a5", "#fc8d62"))


```

